### 2022-01-12 src-latex/parts/00-abstract.tex
Updates from Overleaf

% !TeX root = ../main-paper.tex
The paper features a comparison of a selection (FIXME be more specific/enumerate) of named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
FIXME add numerical results
Results can be reproduced using data and code freely available at \url{https://github.com/soduco/paper-ner-bench-das22}
and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

>>>>

% !TeX root = ../main-paper.tex
This paper features a comparison of four (\bertrand{Ensure it's 4!} named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
FIXME add numerical results
Results can be reproduced using data and code freely available at \url{https://github.com/soduco/paper-ner-bench-das22}
and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

### 2022-01-12 src-latex/parts/30-dataset.tex
Updates from Overleaf

TODO interesting points to detail:
\begin{itemize}
    \item origin
    \item illustration (maybe in first figure)
    \item various numbers (of original data and of the sample we extracted) : number of entries per pages, variety of directory entries, \dots
    \item statistics about entry lengths (histogram of number of char / tokens par entry)
    \item entities we considered and how we annotated them (how we assessed gold's quality)
    \item statistics on the distribution of entities across directories and their arrangement within entries
    \item OCR data (automated systems and clean text + how we created the "clean" text + whether/how we assessed clean text's quality)

    \item \dots
\end{itemize}

>>>>

In this work, we  aim  at  producing  structured  spatio-temporal  data  from the information contained in the 19th century Parisian trade directories. To do this, it is therefore necessary to extract the text from the scans of the directories to be processed and to identify the entries in the various indexing lists used. Then, in each of these entries, the named entities they contain have to be extracted to produce structured spatio-temporal data representing the evolution over time of the people and businesses listed in these directories, their descriptions and their locations. Both of these extraction tasks require data to train and evaluate the OCR and NER approaches identified as potentially relevant: Tesseract and PERO OCR for the OCR task and Spacy, and CamemBERT - pre-trained or fine-tuned - neural models for the NER task.

\subsection{The 19th century Parisian trade directories}

\begin{table}[h!]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Directory publisher or name}} & \multicolumn{1}{c|}{\textbf{Year}} & \multicolumn{1}{c|}{\textbf{\# Col}} & \multicolumn{1}{c|}{\textbf{Index}} & \multicolumn{1}{c|}{\textbf{Entry structure}}                                                                                                       
\\ \hline
Favre \& Duchesne & 1798 & 1 & by occupation & {N [O], SN, SNUM — SEC.} 
\\ \hline
Duverneuil et La Tynna & 1801 & 1 & \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & {N, SN, SNUM. SEC.} 
\\ \hline
{Notables communaux de la Seine} & 1801 & 1 & by name & {N, [O,] SN[, SNUM].}
\\ \hline
Duverneuil et La Tynna & 1805 &	2 &	\begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}}N [(F)], SN, SNUM. — SEC.\\ N [(C)], [(O),] SN, SNUM. — SEC.\end{tabular}
\\ \hline
Duverneuil et La Tynna & 1806 & 2 & \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}} N [(F)], SN, SNUM.\\ N [(C)], SN, SNUM.[ — SEC.]\end{tabular}.
\\ \hline
La Tynna & 1813	& 2	& \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}} N,[O,] SN[, SNUM].\\ N, [(T)] O, SN[, SNUM] [, D].\end{tabular}.
\\ \hline
Panckoucke Comm Dulac & 1820 & 1 & by name & N [(F)], O, [(T),] SN, SNUM[, P] .
\\ \hline
Panckoucke hab Dulac & 1820	& 1 & by name & N [(T)], [O,] SN, SNUM [, D].
\\ \hline
Bottin1 & 1820 & 2	& \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}} N [(F \textbar C)][T], [P], SN, SNUM.\\N [(F \textbar C)][T], O, SN, SNUM. CR\end{tabular}.
\\ \hline
Bottin1 & 1827 & 2	& \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}}N [(F \textbar C)][T], [P], SN, SNUM.\\ N [(F \textbar C)][T], O, SN, SNUM.\end{tabular}.
\\ \hline
Deflandre & 1828 & 2 & \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & \begin{tabular}[c]{@{}l@{}} N [(F \textbar C)][T], [P], SN, SNUM. \\N [(F \textbar C)][T], O, SN, SNUM.\end{tabular}.
\\ \hline
Deflandre & 1829 & 2 & \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & .
\\ \hline
Bottin1 & 1837 & 2	& \begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & .
\\ \hline
Cambon almgene & 1841 & 2 &	\begin{tabular}[c]{@{}l@{}}by occupation\\ by name\end{tabular} & .
\\ \hline
Didot & 1841a &	3 &	by name & .
\\ \hline
Didot & 1841a &	4 & by occupation & .
\\ \hline
Didot & 1851a & 4 & by name & .
\\ \hline
Didot & 1851a & 4 &	by occupation & .
\\ \hline
Didot & 1851a & 5 & by address & .
\\ \hline
Didot & 1854a & 3 &	by name & .
\\ \hline
Didot & 1854a & 4 & by name & .
\\ \hline
Didot & 1854a &	5 & by address & .
\\ \hline
Bottin3 & 1854a & 2 & by name & .
\\ \hline
Bottin3 & 1854a & 4 & by address & .
\\ \hline
Bottin3 & 1854a	& 3 & by occupation & .
\\ \hline
DidotBottin & 1860a	& 3	& by name & .
\\ \hline
DidotBottin & 1861a	& 3	& by name & .
\\ \hline
\end{tabular}%
}
\caption{The directories used to build our dataset. Entry structure is described as follows: N - entry name (person or business); F - first name; T - honorary title; C - civility; O - occupation; P - precision; SN - street name; SNUM - street number; SEC - section; D - district; CR - cross-reference}
\label{tab:my-table}
\end{table}

\subsection{Groundtruth data extraction}

\subsection{Assessing the groundtruth quality}

Our dataset is thus made of excerpts

TODO interesting points to detail:
\begin{itemize}
    \item origin
    \item illustration (maybe in first figure)
    \item various numbers (of the original data and of the sample we extracted) : number of entries per pages, variety of directory entries, \dots
    \item statistics about entry lengths (histogram of number of char / tokens par entry)
    \item entities we considered and how we annotated them (how we assessed gold's quality)
    \item statistics on the distribution of entities across directories and their arrangement within entries
    \item OCR data (automated systems and clean text + how we created the "clean" text + whether/how we assessed clean text's quality)
    \item Measure inter-annotator agreement ? 
    \item Explain charset projection
    \item \dots
\end{itemize}

### 2022-01-12 src-latex/parts/60-results.tex
Updates from Overleaf

\subsection{Experiment 1: Accuracy vs NER approach vs training set size}

@@

\caption{Models F1 score on unseen data vs trainset size}
\centering
\begin{tabular}[t]{lcccccccc}
\toprule
Trainset size (\% of the full trainset) & 0.8 & 1.5 & 3.1 & 6.2 & 12.5 & 25 & 50 & 100\\
\midrule
Cnn & \textbf{0.855} & \textbf{0.885} & \textbf{0.910} & 0.911 & 0.919 & 0.925 & 0.926 & 0.929\\
Camembert & 0.236 & 0.626 & 0.856 & \textbf{0.916} & \textbf{0.930} & 0.933 & \textbf{0.948} & 0.953\\
Camembert+pretraining & 0.190 & 0.685 & 0.889 & 0.913 & \textbf{0.930} & \textbf{0.946} & \textbf{0.948} & \textbf{0.960}\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Experiment 3: Accuracy vs NER approach vs OCR noise}

@@

\begin{table}
\caption{Camembert vs noise}
\centering
\begin{tabular}{ll|ll|l}
                            &                      & \multicolumn{2}{l|}{Training data} &   \\
                            &                      & noisy & clean                      &   \\ 
\cline{1-4}
\multirow{2}{*}{Test data } & noisy                & f1    & f1                         &   \\
                            & clean                & f1    & f1                         &   \\ 
\cline{1-4}
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &   \\
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &  
\end{tabular}
\end{table}

>>>>

\subsection{Experiment 1: NER sensibility to the number of training samples}

@@

\caption{Models F1 score on unseen data vs trainset size}
\centering
\begin{tabular}[t]{lcccccccc}
\toprule
Trainset size (entries) & 49 & 99 & 199 & 398 & 796 & 1593 & 3186 & 6373\\
Trainset size (\% of the full trainset) & 0.8 & 1.5 & 3.1 & 6.2 & 12.5 & 25 & 50 & 100\\
\midrule
Cnn & \textbf{0.855} & \textbf{0.885} & \textbf{0.910} & 0.911 & 0.919 & 0.925 & 0.926 & 0.929\\
Camembert & 0.236 & 0.626 & 0.856 & \textbf{0.916} & \textbf{0.930} & 0.933 & \textbf{0.948} & 0.953\\
Camembert+pretraining & 0.190 & 0.685 & 0.889 & 0.913 & \textbf{0.930} & \textbf{0.946} & \textbf{0.948} & \textbf{0.960}\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Experiment 2: NER in the presence of noisy OCR texts}

@@

\begin{table}[h!]
\caption{Camembert vs noise}
\centering
\begin{tabular}{ll|cc|c}
 & & \multicolumn{2}{c|}{Training data} & \\
 & & noisy & clean &   \\ 
\cline{1-4}
\multirow{3}{*}{Test data}& noisy gold (Tesseract) & f1 & f1 & \\
                            & noisy gold (Pero-OCR) & f1 & f1 & \\ 
                            & reference gold & f1 & f1 & \\ 
\cline{1-4}
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &   \\
                            & \multicolumn{1}{l}{} &       & \multicolumn{1}{l}{}       &  
\end{tabular}
\end{table}
